Robotic Cart System

### 2020-10-06 systemLevelFunctionalRequirements.tex
Fixed sentence in systemLevelFunctionalRequirements
Relaxed wording on requirements

%------------------------------------------------
\section{Requirements and Specifications}
\subsection{Requirements}
The robotic cart system will meet the following requirements:
\begin{enumerate}
    \item Cart must follow remote at a reasonable distance
    \item Cart must be able to travel at a speed reasonable for walking
    \item User must be alerted if cart falls too far behind
    \item Cart must not require line-of-sight to follow remote
    \item Cart must avoid obstacles
\end{enumerate}

\subsection{Specifications}
Based on the requirements, the robotic cart system must meet the following specifications:
\begin{enumerate}
    \item Cart must be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
    \item Cart must be able to travel at 2 m/s
    \item User must be alerted if the cart falls more than 2 meters behind
    \item Cart must be not require line-of-sight to follow remote
    \item Cart must not collide with obstacles while following remote
\end{enumerate}

% %Each of the helicopters we will be using have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).

% Each of the helicopters used will have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).

% \begin{figure}
%   \centering
%   \captionsetup{justification=centering,margin=3cm}
%   \includegraphics{figs/img/QuanserAero}
%   \caption{Quanser Aero 2-DOF Helicopter \newline (\url{https://www.quanser.com/products/quanser-aero/})}
%   \label{fig:QuanserAero}
% \end{figure}
% %
% The tail of the helicopter has a motor that controls its yaw motion.  Similarly, the main rotor changes the pitch of the helicopter.  The directions in which the motors spin will be determined by the polarity of the applied voltages.  This will be regulated by our smart control algorithm.

% \section{Modes of Operations}
% %\label{sec:modesOfOperations}
% We plan on allowing the user to control the helicopter using three modes of operation.  A short description of each mode is given below.

% \begin{enumerate}[\textbf{Mode~\#}1:]
%     \item Allows the user to control the helicopters to a given configuration. For example, setting the pitch to 45 degrees and the yaw to 90 degrees will move the helicopter that much from the initial configuration.
%     \item Allows the user to choose a time varying input signal, so the helicopter will have a wave-like motion shifting from one configuration to another.  Examples include sine and square waves.
%     \item Allows the user to control the algorithm that the user wishes to apply.  They will be able to choose from LQR, LQG, or ADP.
% \end{enumerate}

>>>>

%------------------------------------------------
\section{Requirements and Specifications}
\subsection{Requirements}
The robotic cart system will meet the following requirements:
\begin{enumerate}
    \item Cart should follow remote at a reasonable distance
    \item Cart should be able to travel at a speed reasonable for walking
    \item User should be alerted if cart falls too far behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should avoid obstacles
\end{enumerate}

\subsection{Specifications}
Based on the requirements, the robotic cart system must meet the following specifications:
\begin{enumerate}
    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
    \item Cart should be able to travel at 2 m/s
    \item User should be alerted if the cart falls more than 2 meters behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should not collide with obstacles while following remote
\end{enumerate}
